### 2024-01-28 docs/projects/noj/index.qmd
Noj - rerendered book

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
title: Wolfram Langauge interop with Wolframite
author: Daniel Slutsky

@@

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
Note that to use Wolframite, you need Wolfamite in the dependencies,
and if Wolfraimte fails to find the correct install path automatically,
you may need to have the `WOLFRAM_INSTALL_PATH` environment variable
set up in your system, as explained in
[Wolframite's README](https://github.com/scicloj/wolframite/).

::: {.sourceClojure}
```clojure
(ns index
  (:refer-clojure
   ;; Exclude symbols also used by Wolfram:
   :exclude [Byte Character Integer Number Short String Thread])
  (:require
   [wolframite.core :as wl]
   [wolframite.tools.hiccup :refer [view]]
   [wolframite.base.parse :as parse]
   [wolframite.jlink]
   [scicloj.kindly.v4.kind :as kind]
   [scicloj.kindly.v4.api :as kindly])
  (:import (com.wolfram.jlink MathCanvas KernelLink)
           (java.awt Color Frame)
           (java.awt.event WindowAdapter ActionEvent)))
```
:::

## Init (base example)

::: {.sourceClojure}
```clojure
^:note-to-test/skip

(wl/eval '(Dot [1 2 3] [4 5 6]))
```
:::

::: {.printedClojure}
```clojure
32

```
:::

## Strings of WL code

::: {.sourceClojure}
```clojure
(wl/eval "{1 , 2, 3} . {4, 5, 6}")
```
:::

::: {.printedClojure}
```clojure
32

```
:::

## Def / intern WL fns, i.e. effectively define WL fns as clojure fns:

::: {.sourceClojure}
```clojure
(def W:Plus (parse/parse-fn 'Plus {:kernel/link @wl/kernel-link-atom}))
```
:::

::: {.sourceClojure}
```clojure
(W:Plus 1 2 3)
```
:::

::: {.printedClojure}
```clojure
6

```
:::

... and call it

::: {.sourceClojure}
```clojure
(def greetings
  (wl/eval
   '(Function [x] (StringJoin "Hello, " x "! This is a Mathematica function's output."))))
```
:::

::: {.sourceClojure}
```clojure
(greetings "Stephen")
```
:::

::: {.printedClojure}
```clojure
"Hello, Stephen! This is a Mathematica function's output."

```
:::

## Bidirectional translation
(Somewhat experimental, especially in the wl->clj direction)

::: {.sourceClojure}
```clojure
(wl/->clj! "GridGraph[{5, 5}]")
```
:::

::: {.printedClojure}
```clojure
(GridGraph [5 5])

```
:::

::: {.sourceClojure}
```clojure
(wl/->wl! '(GridGraph [5 5]) {:output-fn str})
```
:::

::: {.printedClojure}
```clojure
"GridGraph[{5, 5}]"

```
:::

## Graphics

::: {.sourceClojure}
```clojure
(view
 '(GridGraph [5 5]))
```
:::

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

# Preface
[Noj](https://scicloj.github.io/noj/) (short for Scinojure)
is an opinionated way to use the emerging Clojure data stack.
It collects a few of the relevant libraries together
and addes some layers of composition on top of them.

### 2024-01-28 docs/projects/noj/ml.qmd
Noj - rerendered book

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8363     -0.2220      0.0278      0.2168      0.6757

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8228     0.2974     6.1291     0.0000 ***
sepal-width         0.6696     0.0822     8.1451     0.0000 ***
petal-length        0.7126     0.0684    10.4175     0.0000 ***
petal-width        -0.5688     0.1563    -3.6381     0.0004 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3192 on 96 degrees of freedom
Multiple R-squared: 0.8711,    Adjusted R-squared: 0.8671
F-statistic: 216.3502 on 4 and 96 DF,  p-value: 1.417e-42

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7943     -0.2312      0.0256      0.2059      0.8735

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.7726     0.3098     5.7220     0.0000 ***
sepal-width         0.6807     0.0824     8.2622     0.0000 ***
petal-length        0.7112     0.0700    10.1639     0.0000 ***
petal-width        -0.5768     0.1582    -3.6467     0.0004 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3230 on 96 degrees of freedom
Multiple R-squared: 0.8500,    Adjusted R-squared: 0.8453
F-statistic: 181.3338 on 4 and 96 DF,  p-value: 2.062e-39
